---
title: "Random Forests Activity"
author: "Chris Okura"
date: "11/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include = FALSE}
library(tidymodels)
library(ISLR)
df <- Carseats
car_recipe <- recipe(Sales ~ ., 
                     data = df) 
```

### 1. Fit a single decision tree to the entire dataset. Report the cross-validated metrics.
```{r}
car_recipe <- recipe(Sales ~ ., 
                     data = df) 

tree_mod <- decision_tree() %>%
  set_engine("rpart") %>%
  set_mode("regression")

tree_wflow <- workflow() %>%
  add_recipe(car_recipe) %>%
  add_model(tree_mod)

folds = vfold_cv(df, v = 5)


tree_fit <- tree_wflow %>%
  fit_resamples(folds)

tree_fit %>% collect_metrics()


```
### 2. Now, tune your decision tree according to cost_complexity, tree_depth, and min_n to identify the best decision tree model. Report the cross-validated metrics. Plot the final tree and interpret the results.
```{r}
tune_spec <- 
  decision_tree(
    cost_complexity = tune(),
    tree_depth = tune(), 
    min_n = tune()
  ) %>% 
  set_engine("rpart") %>% 
  set_mode("regression")

tree_grid <- grid_regular(cost_complexity(),
                          tree_depth(),
                          min_n(),
                          levels = 2)

```


```{r}
 tree_wf <- workflow() %>%
  add_model(tune_spec) %>%
  add_recipe(car_recipe)

tree_res <- 
  tree_wf %>% 
  tune_grid(
    resamples = folds,
    grid = tree_grid
    )

```


```{r}
tree_res %>% collect_metrics() %>% filter(.metric == "rsq") %>% arrange(desc(mean))

```

```{r}
library(rpart.plot)

best_tree <- tree_res %>%
  select_best("rsq")

final_wf <- 
  tree_wf %>% 
  finalize_workflow(best_tree)

tree_fit_1 <- final_wf %>% fit(df)

tree_fitted <- tree_fit_1 %>% 
  pull_workflow_fit()
rpart.plot(tree_fitted$fit)
```

### 3. Determine the best random forest model for these data and report the cross-validated metrics. Is this model better or worse then the single decision tree?

The best random forest model was better than the decision tree model. The random forest model had an r-squared of .715 and the decision tree had an r-squared of .44.

```{r}
forest_mod <- rand_forest(mtry = tune(), trees = tune(), min_n = tune()) %>%
  set_engine("ranger") %>%
  set_mode("regression")

forest_wflow <- workflow() %>%
  add_recipe(car_recipe) %>%
  add_model(forest_mod)

set.seed(1)

forest_res <-
  tune_grid(
    forest_wflow,
    resamples = folds,
    grid = 25,
    control = control_grid(save_pred = TRUE),
            metrics = metric_set(rsq)
  )

forest_res %>% 
  show_best(metric = "rsq")
```

```{r warning = FALSE}
last_rf_mod <- 
  rand_forest(mtry = 5, min_n = 7, trees = 890) %>% 
  set_engine("ranger", importance = "impurity") %>% 
  set_mode("regression")

last_rf_workflow <- 
  forest_wflow %>% 
  update_model(last_rf_mod)

set.seed(1)
last_rf_fit <- 
  last_rf_workflow %>% 
  fit(df)

last_rf_fit %>% pull_workflow_fit()
last_rf_fit %>% extract_fit_parsnip()
```

### 4

```{r}
library(vip)

last_rf_fit %>% 
  pull_workflow_fit() %>% 
  vip(num_features = 20)
```

### 5. Explain what these variable importance scores represent as if you’re describing them to someone who is new to random forests.

The graph shows what variables are most important in determining our target variable Sales. The two most important factors are price and shelve location. 











